---
title: "Performance of Univariate Kernel Density Estimation methods in TensorFlow"
subtitle: ""
author: "Marc Steiner"
institute: "University of Zurich"
date: "2020/11/20 (updated: `r Sys.Date()`)"
knit: (function(input, ...) {
    
    rmarkdown::render(
      input,
      output_dir = '../docs/presentation',
      envir = globalenv()
    )
  })
output:
  xaringan::moon_reader:
    lib_dir: ../docs/presentation/libs
    css: 'xaringan-themer.css'
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(base_color = "#23395b", outfile='../docs/presentation/xaringan-themer.css')
```

class: inverse, center, middle

# Data collection in high energy physics

---

# Data collection in high energy physics

- Large amount of data
- ...

---
# Data collection in high energy physics

## Histograms

- ...
- ...

---
class: inverse, center, middle

# Kernel Density Estimation

---

# Kernel Density Estimation

...

---

# Kernel Density Estimation

## Simple and Linear Binning

...

---

# Kernel Density Estimation

## Fast Fourier Transform

---

# Kernel Density Estimation

## Improved Sheather Jones

...

---

class: inverse, center, middle

# Current state of the art

---

# Current state of the art

...

---

class: inverse, center, middle

# Implementation

---

# Implementation

...

---

class: inverse, center, middle

# Comparison

---

# Comparison

...

---

class: inverse, center, middle

# Conclusion

---

# Conclusion

---

class: inverse, center, middle

# Thank you for listening!



